Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-12 reports/rmarkdown/manuscript/manuscript_template.Rmd
Hide base r plot rarefaction curves

# Extract data frame from the rarecurve object
rare_df_col<- map2(rare_runs, count, ~ggplot_df_fun(.x, .y))
# Create Plot 
rare_plot <- map(rare_df_col, 
              ~ggplot(.x, aes(x = `Sample size`, y = ASV)) +
              theme_bw() +
              scale_color_manual(values=c('tomato', alpha('black', 0.1))) + 
              geom_line(aes(color = Counts, group = Sample)) +
              theme(plot.title = element_text(hjust = 0.5),
                    plot.margin=unit(c(0,0,0.5,0),"cm"))
            )
raremax <- map(seqtabs, ~min(rowSums(.x)))
r_plot <- pmap(list(rare_plot, raremax, limit, title),
               ~ ..1 + xlim(c(0,..3)) +
               labs(title=paste0("Sequencing ", ..4)) +
               geom_vline(xintercept = ..2, 
                          linetype='dashed', 
                          color='slategray' )
)

@@

```{r Print rare curves, fig.width=6, fig.height=10, fig.align="center"}
ggarrange(r_plot[[1]] + theme(axis.title.x=element_blank()),
          r_plot[[3]] + theme(axis.title.x=element_blank()),
          r_plot[[4]] + theme(axis.title.x=element_blank()),
          r_plot[[5]],
          ncol = 1, 
          labels = c("A","B","C","D")
          )
```

**Supp. Figure 10. Rarefraction curves**. **A** Boston 1 sequencing run, **B** Sthlm sequencing run and **C** and **D** shows Boston sequencing run 2 split in two plots showing the CVL visit 2 samples and the the TISSUE visit 3 samples respectively

>>>>

# Extract data frame from the rarecurve object
rare_df_col<- map2(rare_runs, count, ~ggplot_df_fun(.x, .y))
# Create Plot 
rare_plot <- map(rare_df_col, 
              ~ggplot(.x, aes(x = `Sample size`, y = ASV)) +
              theme_bw() +
              scale_color_manual(values=c('tomato', alpha('black', 0.1))) + 
              geom_line(aes(color = Counts, group = Sample)) +
              theme(plot.title = element_text(hjust = 0.5))
            )
raremax <- map(seqtabs, ~min(rowSums(.x)))
r_plot <- pmap(list(rare_plot, raremax, limit, title),
               ~ ..1 + xlim(c(0,..3)) +
               labs(title=paste0("Rarefaction Curve ", ..4)) +
               geom_vline(xintercept = ..2, 
                          linetype='dashed', 
                          color='slategray' )
)

@@

```{r Print rare curves, fig.width=6, fig.height=10, message=F}
grid.arrange(
  r_plot[[1]],
  r_plot[[3]],
  r_plot[[4]],
  r_plot[[5]],
  nrow = 4,
  clip = FALSE
)
```
